\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}
\usepackage{fontawesome}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Ashish Job} \\ \vspace{1pt}
    \small {832-310-5582} $|$ \href{mailto:ashishjob104@gmail.com}{{ashishjob104@gmail.com}} $|$ 
    \href{https://linkedin.com/in/ashish-job/}{{linkedin.com/in/ashish-job}} 
    $|$ \href{https://github.com/Ashishjob}{{github.com/Ashishjob}}
    $|$ \href{https://ashishjob.web.app/}{{ashishjob.web.app}}
    
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Houston - Honor's College}{Aug. 2022 -- May 2025}
      {Bachelor of Science in Computer Science, Minor in Mathematics}{GPA: 4.00}
    \resumeSubheading{Relevant Coursework:}{}{}{}{Introduction to Programming,}{ Computer Science and Programming}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
  
    \resumeSubheading
      {Cybersecurity Intern}{March 2023 -- May 2023}
      {Chrysallis.AI}{Remote}
      \resumeItemListStart
        \resumeItem{Comprehensively evaluated gap analyses of the institution's set policies concerning threat feed monitoring.}
        \resumeItem{Assembled RACI charts as a team lead to communicate responsibilities with fellow team members.}
      \resumeItemListEnd
      
    \resumeSubheading
      {Tutor}{April 2021 -- August 2021}
      {The Tutoring Center}{Sugar Land, TX}
      \resumeItemListStart
        \resumeItem{Instructed 12 students per day in Math and Sciences, with student ages ranging from pre-school to 12th grade.}
        \resumeItem{Utilized Microsoft Excel to communicate with management and coworkers about scheduled times and clients.}
      \resumeItemListEnd
    \resumeSubHeadingListEnd
      
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
    \resumeProjectHeading
          {\textbf{Pokemon Tamagotchi/RPG $|$ Object-Oriented Programming } $|$ \emph{C++, Git, Figma, UML}}{}
          \resumeItemListStart
            \resumeItem{Developed a Tamagotchi game using \textit{OOP} with \textit{C++} and utilized polymorphism and save/load features.}
            \resumeItem{Designed a \textit{UML} Diagram in \textit{Figma} and appropriately communicated the project's plans and source code's base.}
          \resumeItemListEnd

          \resumeProjectHeading
          {\textbf{Portfolio Website $|$ Web Development} $|$ \emph{JavaScript, HTML/CSS}}{}
          \resumeItemListStart
            \resumeItem{Designed a website to showcase personal computer science experiences and projects in various formats and styles.}
            \resumeItem{Hosted the website to allow for public viewing and user experience by utilizing Google's Firebase platform.}
          \resumeItemListEnd
          
      \resumeProjectHeading
          {\textbf{Malayalam MNIST $|$ Neural Network $|$ [In Progress]} $|$ \emph{Python, Docker, PostgreSQL}}{}
          \resumeItemListStart
            \resumeItem{Developed a digital classification system through which all 56 written Malayalam characters can be identified.}
            \resumeItem{Employed a dataset containing written formats of all 56 characters in Malayalam for Python to classify each letter.}
          \resumeItemListEnd

        \resumeProjectHeading
          {\textbf{PassTA $|$ Fullstack Web Application $|$ [In Progress]} $|$ \emph{TypeScript, React.js, TailwindCSS, AWS Cloud, SQL}}{}
          \resumeItemListStart
            \resumeItem{Created a backend login mechanism to provide users who hold the proper TA credentials specialized access.}
            \resumeItem{Accounted for both students and TAs to hold access to resources furthering their specific related needs.}
          \resumeItemListEnd
          
    \resumeSubHeadingListEnd

    

\section{Leadership / Extracurricular}
    \resumeSubHeadingListStart
        \resumeSubheading{CougarCS $|$ \emph{Typescript, React.js, Next.js, TailwindCSS, Git}}{March 2023 -- Present}{Web Dev Committee}{}
            \resumeItemListStart
                \resumeItem{Involved in the Admin Portal Team and Revamp team to assemble or reconfigure the website's front end.}
                \resumeItem{Utilized Git source control to commit to issues, create separate branches, and merge once corrected.}
            \resumeItemListEnd
            \resumeSubheading{CougarAI}{March 2023 -- Present}{DataCON Logistics Director}{}
            \resumeItemListStart
                \resumeItem{Orchestrated the Logistics end of the first AI-based Datathon event to be held at the University of Houston.}
                \resumeItem{Communicated effectively with other directors to set a plan into motion and construct ideas to be accountable for.}
            \resumeItemListEnd
        
    \resumeSubHeadingListEnd


%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, C++, JavaScript, TypeScript, HTML/CSS, Java, SQL} \\
     \textbf{Technologies/Frameworks}{: React, Node.js, Next.js, Github}
    }}
 \end{itemize}

 \section{Honors / Awards}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{}{Dean’s List - Fall 2022 $|$ Dean’s Distinguished Scholar’s List - Fall 2022 $|$ Dean’s Freshman Excellence Award $|$ \\Dean’s List for  the Honor’s College - Fall 2022 $|$ Commended National Merit Scholar $|$ AP Scholar with Distinction $|$ Academic Excellence Scholarship Recipient $|$ Jerrin Alexander Memorial ACT Award $|$}{} \\
    }}
 \end{itemize}


%-------------------------------------------
\end{document}
